`r glue::glue('inferCNV results for {params$library_id} with {params$reference_name} reference')`

### 2025-05-06 analyses/infercnv-consensus-cell-type/template-notebooks/SCPCP000015_explore-infercnv-results.Rmd
wording

We'll make density plots of the predicted CNV events across chromosomes, for each of the normal references:
The panels will be ordered first by the chromosomes with known CNVs, and then in order for the rest of the chromosomes.

>>>>

We'll make density plots of the predicted CNV events across chromosomes:
The panels will be ordered first by the chromosomes with known CNVs, and then in order for the rest of the chromosomes.
